Manuscript for MADA Project

### 2023-04-24 code/analysis_code/exploratoryanalysis.qmd
Updates

### Save plot
```{r}
#save figure
ggsave(filename = here("results","plot_31701_total_black_vax_rate.png"), plot=plot_31701_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","plot_31705_total_black_vax_rate.png"), plot=plot_31705_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","plot_31707_total_black_vax_rate.png"), plot=plot_31707_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","plot_30815_total_black_vax_rate.png"), plot=plot_30815_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","plot_30907_total_black_vax_rate.png"), plot=plot_30907_total_black_vax_rate)
```

>>>>

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31701_total_black_vax_rate.png"), plot=plot_31701_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31705_total_black_vax_rate.png"), plot=plot_31705_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","31707_total_black_vax_rate.png"), plot=plot_31707_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30815_total_black_vax_rate.png"), plot=plot_30815_total_black_vax_rate)
```

@@

### Save plot
```{r}
#save figure
ggsave(filename = here("results","30907_total_black_vax_rate.png"), plot=plot_30907_total_black_vax_rate)
```

### 2023-04-24 products/Manuscript.qmd
Updates

{{< pagebreak >}}

@@

## General Background
Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@grahamrapierHowSmallGeorgia2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

In July 2022, Albany was awarded a 3.9 million dollar grant from the Health and Human Services and the Office of Minority Health in an effort to fund COVID-19 vaccine hesitancy and health literacy programs[]. The Economic Evaluation Research Group (EERG) out of the University of Georgia College of Public Health Department of Health Policy and Management led by Dr. Janani Rajbhandari-Thapa is currently conducting an evaluation on the federally funded programs.

@@

The was no noticiable increase of vaccination rate for

```{r}
knitr::include_graphics("../results/plot_31701_total_black_vax_rate.png")
```

```{r}
knitr::include_graphics("../results/31705_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_total_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_total_black_vax.png")
```

## Vaccination Trends of the Black Community for Each Zip Code by Gender
```{r}
knitr::include_graphics("../results/31701_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_Gender_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_Gender_black_vax.png")
```

## Vaccination Trends of the Black Community for Each Zip Code by Gender
```{r}
knitr::include_graphics("../results/31701_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31705_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/31707_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30815_Age_black_vax.png")
```

```{r}
knitr::include_graphics("../results/30907_Age_black_vax.png")
```

## LASSO Results Visual 
```{r}
knitr::include_graphics("../results/lasso_grid_plot.png")
```

## Final LASSO Results Variable Importance 
```{r}
knitr::include_graphics("../results/final_lasso_plot.png")
```

@@

# Discussion

>>>>

@@

## General Background
Back in March 2020, COVID-19 greatly impacted the citizens of the Albany, GA. Early on in the COVID-19 pandemic Albany, GA was ranked the "forth-worst" city hit by COVID-19 in the United States [@Rapier2020]. According to U.S Census Bureau, 74.5% of the total population of the City of Albany is made up by residents that are black. In a study that examined the health outcomes of residents who tested positive for COVID-19 in Albany, GA it was found that 83.3% of 710 patients that were hospitalized for COVID-19 were black[@Racine2022]. Although there was no differences in hospital mortality found between residents that were black compared to residents that were not black but there was a much higher percentage of hospitalizations due to COVID-19 for residents who were black.

In July 2022, Albany was awarded a 3.9 million dollar grant from the Health and Human Services and the Office of Minority Health in an effort to fund COVID-19 vaccine hesitancy and health literacy programs[@TheAlbanyHerald]. The Economic Evaluation Research Group (EERG) out of the University of Georgia College of Public Health Department of Health Policy and Management led by Dr. Janani Rajbhandari-Thapa is currently conducting an evaluation on the federally funded programs.

@@

### Zip code 31701
The vaccination rate of the the Black population slightly decreased from a rate of 61% to 60.6% \@ref(fig:31701_total_black_vax_rate). The vaccination rate for female black residents slightly decreased from 65% to 64% while the male black resident population's vaccination rate increased slightly at 53% to 57%. It is important to note the difference between the vaccination rates of female and male black residents, which is around .1 from September to February \@ref(fig:31701_Gender_black_vax). When the black population was stratified by age, the rates were the highest for the ages of 65 and older at 89%. Black residents aged 45-64 had a steady rate of 70%, black residents aged 18-44 had a steady rate of 65%, blacked residents aged 10-17 had a steady rate of 40% and black residents aged 5-9 had a steady rate of 12% \@ref(fig:31701_Age_black_vax).

```{r 31701_total_black_vax_rate,  fig.cap='\\label{fig::31701_total_black_vax_rate}Vaccination Rates for Black Population in the 31701 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31701_total_black_vax_rate.png")
```

```{r 31701_Gender_black_vax,  fig.cap='\\label{fig::31701_Gender_black_vax}Vaccination Rates for Black Population by Gender in the 31701 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31701_Gender_black_vax.png")
```

```{r 31701_Age_black_vax.png,  fig.cap='\\label{fig::31701_Age_black_vax}Vaccination Rates for Black Population by Age in the 31701 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31701_Age_black_vax.png")
```

### Zip code 31705
The vaccination rate of stayed stable around 48% for the black population in the 31705 zip code \@ref(fig:31701_Age_black_vax). The vaccination rate of female black residents dropped from 51.1% to 49.7% from September to December, but remained stable close to 50% until February. For male black residents the vaccination rate hovered around 44% \@ref(fig:31705_Gender_black_vax). After stratifying by age the vaccination rates for the 65+, 44-64, 18-44, 10-17 and 5-9 ages groups were as follows: 85%, 68%, 43%, 35% and 12% \@ref(fig:31705_Age_black_vax).

```{r 31705_total_black_vax_rate,  fig.cap='\\label{fig::31705_total_black_vax_rate}Vaccination Rates for Black Population in the 31705 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31705_total_black_vax_rate.png")
```

```{r 31705_Gender_black_vax,  fig.cap='\\label{fig::31705_Gender_black_vax}Vaccination Rates for Black Population by Gender in the 31705 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31705_Gender_black_vax.png")
```

```{r 31705_Age_black_vax,  fig.cap='\\label{fig::31705_Age_black_vax}Vaccination Rates for Black Population by Age in the 31705 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31705_Age_black_vax.png")
```

### Zip code 31707
The total vaccination rate of black residents in the 31707 zip code was around 50% from September through February \@ref(fig:31707_total_black_vax_rate). The vaccination rates for the female and male black population were found to be steady around 54% and 44% \@ref(fig:31707_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 98%, 85%, 52%, 37%, and 17% \@ref(fig:31707_Age_black_vax).

```{r 31707_total_black_vax_rate,  fig.cap='\\label{fig::31707_total_black_vax_rate}Vaccination Rates for Black Population in the 31707 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31707_total_black_vax_rate.png")
```

```{r 31707_Gender_black_vax,  fig.cap='\\label{fig::31707_Gender_black_vax}Vaccination Rates for Black Population by Gender in the 31707 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31707_Gender_black_vax.png")
```

```{r 31707_Age_black_vax,  fig.cap='\\label{fig::31707_Age_black_vax}Vaccination Rates for Black Population by Age in the 31707 Zipcode', echo=FALSE}
knitr::include_graphics("../results/31707_Age_black_vax.png")
```

### Zip code 30815
The total vaccination rate for the black population was 44% in the 30815 zip code from September through February \@ref(fig:30815_total_black_vax_rate). The vaccination rates for black female and male residents were 49% and 38% \@ref(fig:30815_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 78%, 60%, 38%, 31%, and 8% \@ref(fig:30815_Age_black_vax).

```{r 30815_total_black_vax_rate,  fig.cap='\\label{fig::30815_total_black_vax_rate}Vaccination Rates for Black Population in the 30815 Zipcode', echo=FALSE}
knitr::include_graphics("../results/30815_total_black_vax_rate.png")
```

```{r 30815_Gender_black_vax,  fig.cap='\\label{fig::30815_Gender_black_vax}Vaccination Rates for Black Population by Gender in the 30815 Zipcode', echo=FALSE}
knitr::include_graphics("../results/30815_Gender_black_vax.png")
```

```{r 30815_Age_black_vax,  fig.cap='\\label{fig::30815_Age_black_vax}Vaccination Rates for Black Population by Age in the 30815 Zipcode', echo=FALSE}
knitr::include_graphics("../results/30815_Age_black_vax.png")
```

### Zip code 30907
The total vaccination rate for the black population was 54% in September and dropped to around 53% in February in the 30907 zip code \@ref(fig:30907_total_black_vax_rate). The vaccination rates for black female and male residents were 60% and 45% \@ref(fig:30907_Gender_black_vax). The vaccination rates by the age groups 65+, 44-64, 18-44, 10-17 and 5-9 where found to be 95%, 64%, 63%, 33%, and 11% \@ref(fig:30907_Age_black_vax).

```{r 30907_total_black_vax_rate,  fig.cap='\\label{fig::30907_total_black_vax_rate}Vaccination Rates for Black Population in the 30907 Zipcode', echo=FALSE}
knitr::include_graphics("../results/30907_total_black_vax_rate.png")
```

```{r 30907_Gender_black_vax,  fig.cap='\\label{fig::30907_Gender_black_vax}Vaccination Rates for Black Population by Gender in the 30907 Zipcode', echo=FALSE}
knitr::include_graphics("../results/30907_Gender_black_vax.png")
```

```{r 30907_Age_black_vax,  fig.cap='\\label{fig::30907_Age_black_vax}Vaccination Rates for Black Population by Age in the 30907 Zipcode', echo=FALSE}
knitr::include_graphics("../results/30907_Age_black_vax.png")
```

### Statistical Analysis

@@

# Discussion
Albany, Georgia is predominately black

### 2023-04-24 products/supplement.qmd
Updates

@@

@@

@@

        -   `processingcode.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 that was downloaded in September 2022

@@

    -   `Black_Vax_Total.png`: Contains a line graph with all three zip codes plotted for the African American populations

    -   `Black_Vax_Total_31701.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31701 zip code

    -   `Black_Vax_Total_31705.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31705 zip code

    -   `Black_Vax_Total_31707.png`: A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31707 zip code

>>>>

            -   processed_POP_data_31701_Sept.rds`: Contains processed data for the 31701 zip code Total Black Population during September, 2022

            -   processed_POP_data_31701_Oct.rds`: Contains processed data for the 31701 zip code Total Black Population during October, 2022

            -   processed_POP_data_31701_Nov.rds`: Contains processed data for the 31701 zip code Total Black Population during November, 2022

            -   processed_POP_data_31701_Dec.rds`: Contains processed data for the 31701 zip code Total Black Population during December, 2022

            -   processed_POP_data_31701_Jan.rds`: Contains processed data for the 31701 zip code Total Black Population during January, 2023

            -   processed_POP_data_31701_Feb.rds`: Contains processed data for the 31701 zip code Total Black Population during February, 2023

            -   `processed_POP_combined_31701.rds`: Contains Total Population with all variables by month (September-February) for African Americans in the 31701 zip

@@

            -   processed_POP_data_31705_Sept.rds`: Contains processed data for the 31705 zip code Total Black Population during September, 2022

            -   processed_POP_data_31705_Oct.rds`: Contains processed data for the 31705 zip code Total Black Population during October, 2022

            -   processed_POP_data_31705_Nov.rds`: Contains processed data for the 31705 zip code Total Black Population during November, 2022

            -   processed_POP_data_31705_Dec.rds`: Contains processed data for the 31705 zip code Total Black Population during December, 2022

            -   processed_POP_data_31705_Jan.rds`: Contains processed data for the 31705 zip code Total Black Population during January, 2023

            -   processed_POP_data_31705_Feb.rds`: Contains processed data for the 31705 zip code Total Black Population during February, 2023

            -   `processed_POP_combined_31705.rds`: Contains Total Population with all variables by month (September-February) for African Americans in the 31705 zip

@@

            -   processed_POP_data_31707_Sept.rds`: Contains processed data for the 31707 zip code Total Black Population during September, 2022

            -   processed_POP_data_31707_Oct.rds`: Contains processed data for the 31707 zip code Total Black Population during October, 2022

            -   processed_POP_data_31707_Nov.rds`: Contains processed data for the 31707 zip code Total Black Population during November, 2022

            -   processed_POP_data_31707_Dec.rds`: Contains processed data for the 31707 zip code Total Black Population during December, 2022

            -   processed_POP_data_31707_Jan.rds`: Contains processed data for the 31707 zip code Total Black Population during January, 2023

            -   processed_POP_data_31707_Feb.rds`: Contains processed data for the 31707 zip code Total Black Population during February, 2023

            -   `processed_POP_combined_31707.rds`: Contains Total Population with all variables by month (September-February) for African Americans in the 31707 zip

        -   `Zip_30815` folder: Contains processed data for the 31707 zip code
            -   `processed_data_30815_Sept.rds`: Contains processed data for the 30815 zip code during September, 2022

            -   `processed_data_30815_Oct.rds`: Contains processed data for the 30815 zip code during October, 2022

            -   `processed_data_30815_Nov.rds`: Contains processed data for the 30815 zip code during November, 2022

            -   `processed_data_30815_Dec.rds`: Contains processed data for the 30815 zip code during December, 2022

            -   `processed_data_30815_Jan.rds`: Contains processed data for the 30815 zip code during January, 2023

            -   `processed_data_30815_Feb.rds`: Contains processed data for the 30815 zip code during February, 2023

            -   processed_POP_data_30815_Sept.rds`: Contains processed data for the 30815 zip code Total Black Population during September, 2022

            -   processed_POP_data_30815_Oct.rds`: Contains processed data for the 30815 zip code Total Black Population during October, 2022

            -   processed_POP_data_30815_Nov.rds`: Contains processed data for the 30815 zip code Total Black Population during November, 2022

            -   processed_POP_data_30815_Dec.rds`: Contains processed data for the 30815 zip code Total Black Population during December, 2022

            -   processed_POP_data_30815_Jan.rds`: Contains processed data for the 30815 zip code Total Black Population during January, 2023

            -   processed_POP_data_30815_Feb.rds`: Contains processed data for the 30815 zip code Total Black Population during February, 2023

        -   `Zip_30907` folder: Contains processed data for the 31707 zip code

            -   `processed_data_30907_Sept.rds`: Contains processed data for the 30907 zip code during September, 2022

            -   `processed_data_30907_Oct.rds`: Contains processed data for the 30907 zip code during October, 2022

            -   `processed_data_30907_Nov.rds`: Contains processed data for the 30907 zip code during November, 2022

            -   `processed_data_30907_Dec.rds`: Contains processed data for the 30907 zip code during December, 2022

            -   `processed_data_30907_Jan.rds`: Contains processed data for the 30907 zip code during January, 2023

            -   `processed_data_30907_Feb.rds`: Contains processed data for the 30907 zip code during February, 2023
            -   processed_POP_data_30907_Sept.rds`: Contains processed data for the 30907 zip code Total Black Population during September, 2022

            -   processed_POP_data_30907_Oct.rds`: Contains processed data for the 30907 zip code Total Black Population during October, 2022

            -   processed_POP_data_30907_Nov.rds`: Contains processed data for the 30907 zip code Total Black Population during November, 2022

            -   processed_POP_data_30907_Dec.rds`: Contains processed data for the 30907 zip code Total Black Population during December, 2022

            -   processed_POP_data_30907_Jan.rds`: Contains processed data for the 30907 zip code Total Black Population during January, 2023

            -   processed_POP_data_30907_Feb.rds`: Contains processed data for the 30907 zip code Total Black Population during February, 2023

@@

        -   `processingcode.qmd`: processing code for COVID-19 vaccination data in the three target zip codes 31701, 31705 and 31707 and the two control zip codes 30815 and 30907

        -   `processingcode2.qmd`: processing code for COVID-19 Population data in the three target zip codes 31701, 31705 and 31707 and the two control zip codes 30815 and 30907

@@

    -   `31701_total_black_vax_rate.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31701 zip code

    -   `31705_total_black_vax_rate.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31705 zip code

    -   `31707_total_black_vax_rate.png`: A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 31707 zip code

    -   `30815_total_black_vax_rate.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 30815 zip code

    -   `30907_total_black_vax_rate.png` : A line graph of African Americans with at least one dose of the COVID-19 vaccine in the 30907 zip code

    -   `31701_Gender_black_vax.png`: A line graph of African Americans by Gender with at least one dose of the COVID-19 vaccine in the 31701 zip code

    -   `31705_Gender_black_vax.png`: A line graph of African Americans by Gender with at least one dose of the COVID-19 vaccine in the 31705 zip code

    -   `31707_Gender_black_vax.png`: A line graph of African Americans by Gender with at least one dose of the COVID-19 vaccine in the 31707 zip code

    -   `30815_Gender_black_vax.png`: A line graph of African Americans by Gender with at least one dose of the COVID-19 vaccine in the 30815 zip code

    -   `30907_Gender_black_vax.png`: A line graph of African Americans by Gender with at least one dose of the COVID-19 vaccine in the 30907 zip code

    -   `31701_Age_black_vax.png`: A line graph of African Americans by Age with at least one dose of the COVID-19 vaccine in the 31701 zip code

    -   `31705_Age_black_vax.png`: A line graph of African Americans by Age with at least one dose of the COVID-19 vaccine in the 31705 zip code

    -   `31707_Age_black_vax.png`: A line graph of African Americans by Age with at least one dose of the COVID-19 vaccine in the 31707 zip code

    -   `30815_Age_black_vax.png`: A line graph of African Americans by Age with at least one dose of the COVID-19 vaccine in the 30815 zip code

    -   `30907_Age_black_vax.png`: A line graph of African Americans by Age with at least one dose of the COVID-19 vaccine in the 30907 zip code
